ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2016-07-29 asce-paper.tex
conclusions and acknowledgements

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
We present an approach to mitigate this issue, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitary layout using the survival signature.
Our approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
but not for posterior predictive***

However, there is no corresponding reasoning for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

Writing out \eqref{eq:sysrel-survsign}, we get
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.

@@

***if we would also wish to learn about the shape pm, we could follow
standard Bayesian approaches and use a finite discrete distribution for beta - developing this together
with suitable sets of priors for lambda, in particular to show the effect of prior-data conflict, is an interesting
challenge for future research.

***acknowledgements

\pagebreak
%
%
% Now we start the appendices, with the new section name, "Appendix", and a 
%  new counter, "I", "II", etc.
%
\appendix\label{section:references}
%
% Here's the first appendix, the list of references:
%
\bibliography{refs}
%
%\cite{key}   produces citations with full author list and year 
%\citeNP{key} produces citations with full author list and year, but without enclosing parentheses
%\citeA{key}  produces citations with only the full author list
%\citeN{key}  produces citations with the full author list and year, but
%             which can be used as nouns in a sentence; no parentheses appear around
%             the author names, but only around the year
%\citeyear{key}   produces the year information only, within parentheses
%\citeyearNP{key} produces the year information only
%
%
% And now for some pretty impressive notation.  In this example, I have used
%   the tabular environment to line up the columns in ASCE style.
%   Note that this and all appendices (except the references) start with 
%   the \section command
%
\iffalse
\section{Notation}
\emph{The following symbols are used in this paper:}%\par\vspace{0.10in}
\nopagebreak
\par
\begin{tabular}{r  @{\hspace{1em}=\hspace{1em}}  l}
$D$                    & pile diameter (m); \\
$R$                    & distance (m);      and\\
$C_{\mathrm{Oh\;no!}}$ & fudge factor.
\end{tabular}
\fi

>>>>

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
%but not for posterior predictive***
%
However, there is no corresponding reasoning for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

Writing out \eqref{eq:sysrel-survsign}, we get
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\label{eq:sysrel-optim-n0}
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.

@@

In this paper we presented a robust Bayesian approach to reliability estimation for systems of arbitrary layout,
and showed how the use of sets of prior distributions results in increased imprecision,
i.e., more cautious probability statements, in case of prior-data conflict (cases~2 and 3 in Section~\ref{sec:examples}),
while giving more precise reliability bounds when prior and data are in agreement (case~1 in Section~\ref{sec:examples}).
The parameters through which prior information is encoded have a clear interpretation
and are thus easily elicited, either directly or with help of the prior predictive \eqref{eq:tpriopred}.
Calculation of lower and upper predictive system reliability bounds is tractable,
requiring only a simple $K$-dimensional box-constrained optimization in Equation~\eqref{eq:sysrel-optim-n0}.

We think that increased imprecision is an appropriate tool for mirroring prior-data conflict
when considering sets of priors as is done in both the robust Bayesian and imprecise probability framework.
We want to emphazise, however, that this tool may be useful already
for just highlighting `conflict' between multiple information sources,
and that we do not think that the resulting set of posteriors,
although it can form a meaningful basis, must necessarily be used
for all consequential inferences, as a strict Bayesian would posit.
We believe an analyst is free to reconsider any aspect of a model
(of which the choice of prior can be seen to form a part) after seeing the data,
and so may use our method only for becoming aware of a conflict between prior and data.

The robust Bayesian setting we employed provides many further modelling opportunities
beyond the explicit reaction to prior-data conflict.
These opportunities have not yet been explored and
provide a wide field for further research.
An example is our currently ongoing investigation into
extending the present model to allow also for an appropriate reflection of very strong agreement between prior and data
\cite{ipmu2016}.

There are many aspects to further develop in our analysis and modeling.
Straightforward to implement is, e.g., the analysis of the effect of replacing failed components
in the system on system reliability bounds. %the reliability quantification $[\lRsys(t \mid T > \tnow), \uRsys(t \mid T > \tnow)]$.
Criteria for the trade-off between the cost of replacement and the gain in reliability
would have to be adapted for the interval output of our model,
leading to very interesting research questions.
%
To estimate the shape parameters $\beta_k$ together with the scale parameters $\lambda_k$,
one could follow standard Bayesian approaches and use a finite discrete distribution for $\beta_k$.
Developing this together with suitable sets of priors for $\lambda_k$,
in particular to show the effect of prior-data conflict, is another interesting challenge for future research.
%
Another further important aspect in system reliability we have not accounted for yet
is the possibility of common-cause failures,
i.e., failure events where several components fail at the same time due to a shared or common root cause.
This could be done by combining the common-cause failure model approaches
of \citeN{Troffaes2014a} and \citeN{2015:coolen-commoncause}.

On a more abstract level, the choice for the set of prior parameters
(generating the set of prior component failure distributions) as $[\nkzl, \nkzu] \times [\ykzl, \ykzu]$
has the advantage of allowing for easy elicitation and tractable inferences,
but it may not be suitable to reflect certain kinds of prior knowledge.
Also, as studied in \cite{Walter2011a} and \cite[\S 3.1]{diss},
the shape of the prior parameter set has a crucial influence on model behaviour
like the severity of prior-data conflict reaction.
As noted in \cite[pp.~66f]{diss},
more general prior parameter set shapes are possible in principle,
but may be more difficult to elicit and make calculations more complex.

\section*{Acknowledgements}

Gero Walter was supported by the DINALOG project CAMPI
(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').

%\pagebreak
%
%
% Now we start the appendices, with the new section name, "Appendix", and a 
%  new counter, "I", "II", etc.
%
\appendix\label{section:references}
%
% Here's the first appendix, the list of references:
%
\bibliography{refs}
%
%\cite{key}   produces citations with full author list and year 
%\citeNP{key} produces citations with full author list and year, but without enclosing parentheses
%\citeA{key}  produces citations with only the full author list
%\citeN{key}  produces citations with the full author list and year, but
%             which can be used as nouns in a sentence; no parentheses appear around
%             the author names, but only around the year
%\citeyear{key}   produces the year information only, within parentheses
%\citeyearNP{key} produces the year information only
%
%
% And now for some pretty impressive notation.  In this example, I have used
%   the tabular environment to line up the columns in ASCE style.
%   Note that this and all appendices (except the references) start with 
%   the \section command
%
\iffalse
\section{Notation}
\emph{The following symbols are used in this paper:}%\par\vspace{0.10in}
\nopagebreak
\par
\begin{tabular}{r  @{\hspace{1em}=\hspace{1em}}  l}
$D$                    & pile diameter (m); \\
$R$                    & distance (m);      and\\
$C_{\mathrm{Oh\;no!}}$ & fudge factor.
\end{tabular}
\fi
